\documentclass[12pt]{article}
\usepackage{amsfonts, epsfig}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lfoot{\texttt{emamtm0067.github.io}}
\lhead{Introduction to AI - Coursework}
\rhead{\thepage}
\cfoot{}
\begin{document}

\section*{Coursework }

\subsection*{Question 1 (25 pts)}

The idea for this question is to cluster words; for the question you
will need a substantial piece of text. I suggest you use Project
Gutenberg\\ \\ \texttt{https://www.gutenberg.org/} \\ \\ and download
a few novels and concatenate them. Try to pick reasonably recent
novels since they will have a more contemporary language use, however,
because of the copyright restrictions the books tend to older. In what
follows there are a series of ``marking waypoints'' indicated with
numbers in square brackets of the form [m1] to [m6], these will be
explained after the overall requirements are discussed.

When you have created your text [m1] pick a set of about 100 words,
these should not be function words like ``the'' or ``of'', so, for
example, pick 100 nouns or a set split between nouns, verbs, adjective
and adverbs. These might be the most common words in these classes or
they may all be words in a specitic category, abstract nouns for
example, or words related to needlework [m2]. Call this list $L$.

Now we want to create a set of similarities or distances between pairs
of words in $L$. The similarity I have in mind is how often two words
occur in the same sentence, or the average distance apart the words
are in the text [m3]. Use this distance or similarity measure to
perform unsupervised learning, any algorithm you want, and describe
the results [m4].

The distance between two words may be greater than distance you get if
you go by way of a third word: for example, and this example is a
completely made up, image
\begin{align}
  d(\text{soup},\text{bed})&=34.4\\
  d(\text{soup},\text{spoon})&=2.8\\
  d(\text{spoon},\text{bed})&=4.6
\end{align}
Now it is quicker to get from soup to bed if you go by way of spoon and it might be more correct to regard
\begin{equation}
  d(\text{soup},\text{bed})=2.8+4.6=7.4
\end{equation}
Use Dijkstra's algorithm to find the shortest distance between an pair
of words in $L$ [m5] and repeat the unsupervised learning. Is it any
different? [m6]


The mark waypoints [m1]-[m6] are there to give an idea of the marking
scheme but is intended to be a rough guide, not a rigid scheme. At
[m1] four marks will have been allocated, to get a particularly good
mark here make sure the data has been cleaned. At [m2] an additional
two marks have been allocated, as an aside, this is a place an LLM
could sensibly be used, for example, to pick the nouns from a list. At
[m3] another four marks have been allocated, be careful to explain how
you are calculating the distance, why you made that choice and what
you see, for example, by noting which words are closest and which
furthest apart. Six more marks are allocated by [m4], for a very
good mark discuss the choice of algorithm and any meta-parameters, use
graphs to compare different choices. Six more marks are allocated by
[m5]; obviously the challenge here is implementing the
algorithm. Explain clearly what you have done. Finally there are three
more marks to be allocated by [m6].

\subsection*{Question 3 (15 marks)}

Generate a data set in two dimensions with a division boundary of the
form $y=ax^2+x$, so points one side of this boundary belong to class A
and to the other, class B. Investigate how well logistic regression
works for these data as $a$ is varied. What about a small neural
network? How are these approaches affected if the number of points is
varied, or the balance between class A and class B in the number of
points? How does changing the size of the network change the performance.


\subsection*{Question 3 (10 marks)}

Do large language models have rights or other attributes of
personhood? Do they have rights and will they acquire them? Discuss this in an essay of about one page.

\begin{itemize}
\item Your essay should stay focused on that topic throughout. 
\item If you argue for or against a position, ensure your points directly support your stance. If you're presenting both sides, weigh the pros and cons.
\item Start with a clear introduction that states your main argument or the scope of your discussion.
\item Organise your points logically in the body of your essay. Each paragraph should advance your argument or analysis.
\item Conclude with a summary of your argument or final reflection on the topic.
\item Reference key studies or theories that support your argument. Provide brief explanations of why the cited studies are important for your argument.
\item  Don't just summarise; engage critically with the literature.
\item For higher marks, address counterarguments or limitations in the approaches you're discussing.
\item Aim for clear and precise writing. Avoid jargon unless necessary and explain technical terms.
\item Ensure that your essay is free of grammatical and spelling errors, and that your ideas flow smoothly from one to the next.
\end{itemize}

You can use AI in helping develop your thoughts, or for finding and
fixing errors, but I expect clarity, originality and incisive thought
with strong, clearly held views while avoiding platitudes and weasel
statements. None of this will be present in an essay which has, from
the start, been taken from an LLM.


\subsection*{Report}

Your report should be no longer than seven pages, excluding any
references. Use an 11 or 12pt font and use a standard page layout, do
not expand the page just to make it fit more text!

Your report must be submitted in pdf and should be prepared in LaTeX;
overleaf is a good approach, but not required as long as LaTeX has
been used\footnote{R-markdown and some other notebook-based
environments typeset using LaTeX, this is acceptable}. As always when
using LaTeX, give yourself over to defaults, our expectation of what a
document should look like has been conditioned on LaTeX, so it is best
not to try to override the look of the document.

Avoid code snippets in the report unless that feels like the best way
to illustrate some subtle aspect of an algorithm; do always though
consider a mathematical description if possible. You will be asked to
submit code and it may be tested to make sure it works and matches
your report. It will not, however, be marked in and of itself.

\subsection*{Submission}

The deadline for report and code: 13h00 (GMT+1) on Monday 2025-04-28, there
will be a submission point on Blackboard under the ``assessment,
submission and feedback'' link. Please upload the following two files:
\begin{enumerate}
\item Your report as a PDF with filename <student\_number>.pdf, where
  ``<student\_number'' is replaced by your student number, not your
  username. Upload this to the submission point ``Introduction to AI
  Coursework (Turnitin)''.
\item Your code inside a single zip file with filename
  <student\_number>.zip. Inside the zip file there should be a single
  folder containing your code, with your student number as the folder
  name. Please remove datasets and other large files to minimise the
  upload size - we only need the code itself. Upload this file to the
  submission point ``Code for Introduction to AI Coursework''.
\end{enumerate}
  
We may review your Python code by eye but your marks will be based on
the contents of your report, with the code used to check how you
carried out the experiments described in your report. We will not give
marks for the coding style, comments, or organisation of the
code. Code written in Julia or R is also acceptable as is the use of a
standard notebook format. If you are particularly keen on another
programming language let me know and I will consider this.

Please do not include your name in the report text itself: to ensure
fairness, we mark the reports anonymously.

Avoiding Academic Offences: Please re-read the university's plagiarism
rules to make sure you do not break any rules. Academic offences
include submission of work that is not your own, falsification of data
/ evidence or the use of materials without appropriate
referencing. Note that sharing your report with others is also not
allowed. These offences are all taken very seriously by the University
and we have very little leeway within the framework the University has
set out. Do not copy text directly from your sources - always rewrite
in your own words and provide a citation. Work independently -- do not
share your code or reports with others; you can, of course, discuss
your work with your classmates, but do not share text or code.

Suspected offences will be dealt with in accordance with the
University's policies and procedures. If an academic offence is
suspected in your work, you will be asked to attend an interview with
senior members of the school, where you will be given the opportunity
to defend your work. The plagiarism panel can apply a range of
penalties, depending on the severity of the offence. These include a
requirement to resubmit work, capping of grades and the award of no
mark for an element of assessment. Again, we are not in a position to
be lenient here, the academic offences procedure is not one we control.

\subsection*{Extensions and Exceptional Circumstances}

If the completion of your assignment has been significantly disrupted
by serious health conditions or personal problems, or other serious
issues, you can apply for consideration in accordance with the normal
university policy and processes. Students should refer to the guidance
and complete the application forms as soon as possible when the
problem occurs. Please see the guidance below and discuss with your
personal tutor for more advice:
\begin{itemize}
\item \texttt{www.bristol.ac.uk/students/support/academic-advice/\\
  assessment-support/request-a-coursework-extension/}
\item \texttt{www.bristol.ac.uk/students/support/academic-advice/\\assessment-support/exceptional-circumstances/}
    \end{itemize}



\end{document}
